\documentclass[leqno]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage[parfill]{parskip}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amssymb}

\title{Computationele logica}
\author{
    Kamans, Jim\\
    \texttt{10302905}
    \and
    Roosingh, Sander\\
    \texttt{11983957}
    \and
    Schenk, Stefan\\
    \texttt{11881798}
}
\date{December 2017}

\begin{document}

\maketitle

\textbf{Possibility:} $\sim_a \coloneqq \leq_a \cup \geq_a$

\textbf{Information Cell:} $w(a) \coloneqq \{s\in W:w\sim_a s\}$

\textbf{Knowledge:} $\lVert K_a \varphi \rVert_M = \{s\in W:s(a) \subseteq
\lVert \varphi \rVert_M\}$

\textbf{Conditional Belief:} $\lVert B_a^\varphi \psi \rVert_M = \{s \in
W:best_a(\lVert\varphi\rVert_M \cap s(a)) \subseteq \lVert\psi\rVert_M\}$


%%%%%%%%%%%%%%%%
%% Exercise 1 %%
%%%%%%%%%%%%%%%%
\section*{Exercise 1}

\textit{(a) Show the following equivalence:}
\begin{center}
    $K_a \varphi \Leftrightarrow B_a^{\neg \varphi} false$
\end{center}

Take $s \in W$ such that $s \models_M K_a \varphi$.

Therefore for all $t \in s(a)$ it's true that: $t \models_M
\varphi$.

Using conditional belief:
$\lVert B_a^{\neg \varphi}false\rVert_M=\{v\in W:best_a(\lVert\neg\varphi\rVert_M\cap v(a))\subseteq\lVert false\rVert_M\}$

Eliminating any world or all worlds either results in a world from s(a), where $K_a \varphi$, or no worlds at all, so $false$.

% TODO: Nog niet af
[ANSWER HERE] \\


\textit{(b) Prove semantically the equivalence claimed on Slide 24 of Lecture
Notes 4.2:}
\begin{center}
    $B_a \phi \Leftrightarrow \lozenge_a \square_a \phi$
\end{center}
where $\Diamond a \phi : \neg \square a \neg \phi$ is the dual modality to safe
belief $\square a$.





\textit{(c) Prove (via a counterexample) that safe belief does NOT imply strong
belief; i.e. that}
\begin{center}
    $\square_a \varphi \nRightarrow Sb_a \varphi$
\end{center}

The thought that Albert can be drunk can only be gained by new information, but
it's not strongly believed initially:

\begin{center}
\begin{tikzpicture}[scale=0.2]
\tikzstyle{every node}+=[inner sep=0pt]
\draw [black] (7.55,-6.55) circle (3);
\draw (7.55,-6.55) node {$d,\mbox{ }g$};
\draw [black] (18.35,-6.55) circle (3);
\draw (18.35,-6.55) node {$d,\mbox{ }~g$};
\draw [black] (29.55,-6.55) circle (3);
\draw (29.55,-6.55) node {$~d,\mbox{ }g$};
\draw [black] (10.55,-6.55) -- (15.35,-6.55);
\fill [black] (15.35,-6.55) -- (14.55,-6.05) -- (14.55,-7.05);
\draw [black] (21.35,-6.55) -- (26.55,-6.55);
\fill [black] (26.55,-6.55) -- (25.75,-6.05) -- (25.75,-7.05);
\end{tikzpicture}
\end{center}

\textbf{HINT}: The positive statements (a) and (b) need general proofs: you
need to show that, for every plausibility model and every sentence $\phi$, the
desired formula is true at all the worlds of that model. But the negative
statement (c) must be shown by giving a counterexample: construct some
plausibility model and find some sentence $\varphi$ for which the implication
fails to be true at some world of that model (which we can think of as the
“real world”).

%%%%%%%%%%%%%%%%
%% Exercise 2 %%
%%%%%%%%%%%%%%%%
\section*{Exercise 2}

A virtual agent in a video game doesn't know his current position in the 
virtual space, but all he cares is (a) whether or not he's in a ``Dangerous''
zone (say, close to a dangerous monster), and (b) whether or not he's close to 
this Target (say, a treasure). Let's use the letter $d$ to denote the sentence 
\textit{the agent is in a dangerous zone}, and the letter $t$ to denote the 
sentence \textit{the agent is close to the target}. These possibilities are 
independent of each other, and the agent \textbf{doesn't know} which is the 
case, so he \textbf{cannot exclude any} of the four possible cases $d \land t$,
 $d \land \neg t$, $\neg d \land t$ and $\neg d \land \neg t$. However, our 
agent \textbf{believes both} that he's close to the target AND that he's NOT in
 a dangerous zone. \textbf{If} he would learn that this belief is WRONG (i.e. 
that at least one of his two beliefs is false), then he'd still believe (
conditional on this new information) that he is close to the target. But 
\textbf{if} he would learn instead that he's far from (=NOT close to) the 
target, then (conditional on this information) he'd keep his initial belief 
that he's NOT in a dangerous zone.

\begin{enumerate}
    \item \textit{Write down a logical formula in the language of beliefs,
    knowledge and conditional beliefs to encode all the above assumptions.}
    
    $\neg K(t) \land \neg K(\neg t) \land \neg K(d) \land \neg K(\neg d) \land
    B(t \land \neg d) \land B^{\neg (t \land \neg d)}(t) \land 
    B^{\neg t}(\neg d)$

    \item \textit{Represent the agent's beliefs (and conditional beliefs),
    using a \textbf{plausibility model} with four possible worlds. Specify the 
    \textbf{valuation} (which atomic sentences of the two atomic sentences $d$ 
    and $t$ are true at which worlds). Represent the agent's 
    \textbf{plausibility relation} on these worlds, by drawing arrows going 
    from the less plausible worlds to the more plausible ones.}

    \begin{center}
    \begin{tikzpicture}[scale=0.2]
    \tikzstyle{every node}+=[inner sep=0pt]
    \draw [black] (51.233,-16.211) circle (3);
    \draw (51.23,-16.21) node {$t, \, d$};
    \draw [black] (24.133,-16.211) circle (3);
    \draw (24.13,-16.21) node {$\neg t, \, d$};
    \draw [black] (64.056,-16.211) circle (3);
    \draw (64.06,-16.21) node {$t, \, \neg d$};
    \draw [black] (38.156,-16.211) circle (3);
    \draw (38.156,-16.211) node {$\neg t, \, \neg d$};
    \draw [black] (54.23,-16.21) -- (61.06,-16.21);
    \fill [black] (61.06,-16.21) -- (60.26,-15.71) -- (60.26,-16.71);
    \draw [black] (27.13,-16.21) -- (35.16,-16.21);
    \fill [black] (35.16,-16.21) -- (34.36,-15.71) -- (34.36,-16.71);
    \draw [black] (41.16,-16.21) -- (48.23,-16.21);
    \fill [black] (48.23,-16.21) -- (47.43,-15.71) -- (47.43,-16.71);
    \end{tikzpicture}
    \end{center}

    \item \textit{Suppose somebody who never lies tells our agent ``You are 
    close to the target if and only if you believe that you are in a dangerous 
    zone.'' \textbf{Write down formally} this sentence as a formula $\varphi$ 
    in doxastic logic (using the atomic sentences).}

    $\varphi \coloneqq t \leftrightarrow B(d)$

    \item \textit{Interpreting the above truthful announcement $!\varphi$ as an
     \textbf{update} with the sentence $\varphi$ in the previous part, 
    represent the \textbf{updated model}.}

    \begin{center}
    \begin{tikzpicture}[scale=0.2]
    \tikzstyle{every node}+=[inner sep=0pt]
    %\draw [black] (51.233,-16.211) circle (3);
    %\draw (51.23,-16.21) node {$t, \, d$};
    \draw [black] (24.133,-16.211) circle (3);
    \draw (24.13,-16.21) node {$\neg t, \, d$};
    %\draw [black] (64.056,-16.211) circle (3);
    %\draw (64.06,-16.21) node {$t, \, \neg d$};
    \draw [black] (38.156,-16.211) circle (3);
    \draw (38.156,-16.211) node {$\neg t, \, \neg d$};
    %\draw [black] (54.23,-16.21) -- (61.06,-16.21);
    %\fill [black] (61.06,-16.21) -- (60.26,-15.71) -- (60.26,-16.71);
    \draw [black] (27.13,-16.21) -- (35.16,-16.21);
    \fill [black] (35.16,-16.21) -- (34.36,-15.71) -- (34.36,-16.71);
    %\draw [black] (41.16,-16.21) -- (48.23,-16.21);
    %\fill [black] (48.23,-16.21) -- (47.43,-15.71) -- (47.43,-16.71);
    \end{tikzpicture}
    \end{center}

    \item \textit{After the previous announcement, another truthful 
    announcement is made: ``You are in a dangerous zone if and only if you 
    don't believe that you are in a dangerous zone.'' \textbf{Write down 
    formally} this sentence as a formula $\psi$ in doxastic logic (using the 
    atomic sentences).}

    $\psi \coloneqq d \leftrightarrow \neg B(d)$

    \item \textit{\textbf{What is the real world}? (In other words, answer the 
    question: is the agent in a dangerous zone or not, and is he close to the 
    target or not?) \textbf{Justify your answer}, by interpreting the 
    announcement in the previous part as a new update $!\psi$ and 
    \textbf{representing the updated model}.}

	Let S be the model of question 2.4. In S, $\psi$ holds only in world 
	$(\neg t, \, d)$. In this world, $d$ is true and $\neg B(d)$ is true (because 
	$B(d)$ is false, the agent believes $B(\neg d)$). In the other world, 
	$(\neg t, \, \neg d)$, $d$ is false but $\neg B(d)$ is true, so $\psi$ doesn't
	 hold here. Because $\psi$ is truthful, the real world is $(\neg t, \, d)$.

    \begin{center}
    \begin{tikzpicture}[scale=0.2]
    \tikzstyle{every node}+=[inner sep=0pt]
    % \draw [black] (51.233,-16.211) circle (3);
    % \draw (51.23,-16.21) node {$t, \, d$};
    \draw [black] (24.133,-16.211) circle (3);
    \draw (24.13,-16.21) node {$\neg t, \, d$};
    % \draw [black] (64.056,-16.211) circle (3);
    % \draw (64.06,-16.21) node {$t, \, \neg d$};
    % \draw [black] (38.156,-16.211) circle (3);
    % \draw (38.156,-16.211) node {$\neg t, \, \neg d$};
    % \draw [black] (54.23,-16.21) -- (61.06,-16.21);
    % \fill [black] (61.06,-16.21) -- (60.26,-15.71) -- (60.26,-16.71);
    % \draw [black] (27.13,-16.21) -- (35.16,-16.21);
    % \fill [black] (35.16,-16.21) -- (34.36,-15.71) -- (34.36,-16.71);
    % \draw [black] (41.16,-16.21) -- (48.23,-16.21);
    % \fill [black] (48.23,-16.21) -- (47.43,-15.71) -- (47.43,-16.71);
    \end{tikzpicture}
    \end{center}

\end{enumerate}

\end{document}
